### 2017-12-01 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

\begin{tikzpicture}[every edge quotes/.append style={auto, text=black},scale=0.7]
  \pgfmathsetmacro{\cubex}{5}
  \pgfmathsetmacro{\cubey}{5}
  \pgfmathsetmacro{\cubez}{5}
  \draw [arrow] (-1,-1,1) -- (0,-1,1) node[below] {$C_{x\mathsmaller{1}}$};
  \filldraw [red] (-1,-1,1) circle (6pt);
  \draw [draw=black, every edge/.append style={draw=black, densely dashed, opacity=.5}]
    (0,0,0) coordinate (o) -- ++(-\cubex,0,0) coordinate (a) -- ++(0,-\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubez)  -- ++(\cubex,0,0) coordinate (c) -- cycle
    (o) -- ++(0,0,-\cubez) coordinate (d) -- ++(0,-\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
    (o) -- (a) -- ++(0,0,-\cubez) coordinate (f) edge (g) -- (d) -- cycle;
  \path [every edge/.append style={draw=black, |-|}]
    (b) +(0,-5pt) coordinate (b1) edge ["l"'] (b1 -| c)
    (b) +(-5pt,0) coordinate (b2) edge ["l"] (b2 |- a)
    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["l"'] ([xshift=3.5pt,yshift=-3.5pt]e)
    ;
\end{tikzpicture}
\\
\textcolor{red}{Newton's $3^{\text{rd}}$ law - Every action has an equal and opposite reaction}\\
$\Delta mc=mc_{x1}--mc_{x1}=2mc_{x1}$\\
\\
\\
\textcolor{red}{Use $\text{Velocity}=\dfrac{\text{Distance}}{\text{Time}}$}\\
Time=$\dfrac{\text{Distance}}{\text{Velocity}}=\dfrac{2l}{c_{x1}}$\\
\\
\\
\textcolor{red}{Use force$=\dfrac{\text{Change in momentum}}{\text{time}}$}\\
$\text{Force}=\dfrac{\Delta mc}{\Delta t}=\dfrac{2mc{x1}}{2l/c_{x1}}=\dfrac{mc_{x1}^2}{l}$\\
\\
\\
\textcolor{red}{Use Pressure$=\dfrac{\text{Force}}{\text{Area}}$}\\
\\
$p_1=\dfrac{mc_{x1}^2/l}{l^2}=\dfrac{mc_{x1}^2}{l^3}$\\
\\
\\
\textcolor{red}{Expand for N particles}\\
$p=\Sigma p_n=p_1+p_2+p_3...+p_N$\\
\\
$p=\dfrac{mc_{x1}^2}{l^3}+\dfrac{mc_{x2}^2}{l^3}+\dfrac{mc_{x3}^2}{l^3}+\dfrac{mc_{xN}^2}{l^3}$\\
\\
$p=\dfrac{m}{l^3}(c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2)$\\
\\
\\
\textcolor{red}{The mean of all the squares of the velocities is written as $\mathlarger{\bar{c_x^2}}$}\\
\\
$\mathlarger{\bar{c_x^2}}=\dfrac{c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2}{N}$\\
\\
$N\mathlarger{\bar{c_x^2}}=c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2$\\
\\
\\
\textcolor{red}{Simplify expression for pressure}\\
\\
$p=\dfrac{Nm\mathlarger{\bar{c_x^2}}}{l^3}$\\
\\
\\
\\
\textcolor{red}{Consider in 3 dimensions}\\
\\
$\mathlarger{\bar{c^2}=\bar{c_x^2}+\bar{c_y^2}+\bar{c_z^2}}$\\
\\
\\
\textcolor{red}{Average of mean square velocity for each dimension are equal}\\
\\
$\mathlarger{\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
\\
\\
\textcolor{red}{Simplify 3D formula}\\
\\
$\mathlarger{\dfrac{\bar{c^2}}{3}=\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
\\
\\
\textcolor{red}{Simplify pressure formula}\\
\\
$p=\dfrac{1}{3}\times\dfrac{Nm\mathlarger{\bar{c^2}}}{l^3}$\\
\\
\\
\textcolor{red}{Insert Density formula}\\
\\
$\rho=\dfrac{\text{Mass}}{\text{Volume}}=\dfrac{Nm}{l^3}$
\\
\\
\\
\textcolor{red}{Substitute into Pressure formula}\\
\\
$$p=\frac{1}{3}\rho\mathlarger{\bar{c^2}}$$
\end{document}

>>>>

\begin{tikzpicture}[every edge quotes/.append style={auto, text=black},scale=0.7]
  \pgfmathsetmacro{\cubex}{5}
  \pgfmathsetmacro{\cubey}{5}
  \pgfmathsetmacro{\cubez}{5}
  \draw [arrow] (-1,-1,1) -- (0,-1,1) node[below] {$C_{x\mathsmaller{1}}$};
  \filldraw [red] (-1,-1,1) circle (6pt);
  \draw [draw=black, every edge/.append style={draw=black, densely dashed, opacity=.5}]
    (0,0,0) coordinate (o) -- ++(-\cubex,0,0) coordinate (a) -- ++(0,-\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubez)  -- ++(\cubex,0,0) coordinate (c) -- cycle
    (o) -- ++(0,0,-\cubez) coordinate (d) -- ++(0,-\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
    (o) -- (a) -- ++(0,0,-\cubez) coordinate (f) edge (g) -- (d) -- cycle;
  \path [every edge/.append style={draw=black, |-|}]
    (b) +(0,-5pt) coordinate (b1) edge ["$l$"'] (b1 -| c)
    (b) +(-5pt,0) coordinate (b2) edge ["$l$"] (b2 |- a)
    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["$l$"'] ([xshift=3.5pt,yshift=-3.5pt]e)
    ;
\end{tikzpicture}
\\
\textcolor{red}{Newton's $3^{\text{rd}}$ law - Every action has an equal and opposite reaction}\\
$\Delta mc=mc_{x1}--mc_{x1}=2mc_{x1}$\\
\\
\\
\textcolor{red}{Use $\text{Velocity}=\dfrac{\text{Distance}}{\text{Time}}$}\\
Time=$\dfrac{\text{Distance}}{\text{Velocity}}=\dfrac{2l}{c_{x1}}$\\
\\
\\
\textcolor{red}{Use force$=\dfrac{\text{Change in momentum}}{\text{time}}$}\\
$\text{Force}=\dfrac{\Delta mc}{\Delta t}=\dfrac{2mc{x1}}{2l/c_{x1}}=\dfrac{mc_{x1}^2}{l}$\\
\\
\\
\textcolor{red}{Use Pressure$=\dfrac{\text{Force}}{\text{Area}}$}\\
\\
$p_1=\dfrac{mc_{x1}^2/l}{l^2}=\dfrac{mc_{x1}^2}{l^3}$\\
\\
\\
\textcolor{red}{Expand for N particles}\\
$p=\Sigma p_n=p_1+p_2+p_3...+p_N$\\
\\
$p=\dfrac{mc_{x1}^2}{l^3}+\dfrac{mc_{x2}^2}{l^3}+\dfrac{mc_{x3}^2}{l^3}+\dfrac{mc_{xN}^2}{l^3}$\\
\\
$p=\dfrac{m}{l^3}(c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2)$\\
\\
\\
\textcolor{red}{The mean of all the squares of the velocities is written as $\mathlarger{\bar{c_x^2}}$}\\
\\
$\mathlarger{\bar{c_x^2}}=\dfrac{c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2}{N}$\\
\\
$N\mathlarger{\bar{c_x^2}}=c_{x1}^2+c_{x2}^2+c_{x3}^2...+c_{xN}^2$\\
\\
\\
\textcolor{red}{Simplify expression for pressure}\\
\\
$p=\dfrac{Nm\mathlarger{\bar{c_x^2}}}{l^3}$\\
\\
\\
\\
\textcolor{red}{Consider in 3 dimensions}\\
\\
$\mathlarger{\bar{c^2}=\bar{c_x^2}+\bar{c_y^2}+\bar{c_z^2}}$\\
\\
\\
\textcolor{red}{Average of mean square velocity for each dimension are equal}\\
\\
$\mathlarger{\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
\\
\\
\textcolor{red}{Simplify 3D formula}\\
\\
$\mathlarger{\dfrac{\bar{c^2}}{3}=\bar{c_x^2}=\bar{c_y^2}=\bar{c_z^2}}$\\
\\
\\
\textcolor{red}{Simplify pressure formula}\\
\\
$p=\dfrac{1}{3}\times\dfrac{Nm\mathlarger{\bar{c^2}}}{l^3}$\\
\\
\\
\textcolor{red}{Insert Density formula}\\
\\
$\rho=\dfrac{\text{Mass}}{\text{Volume}}=\dfrac{Nm}{l^3}$
\\
\\
\\
\textcolor{red}{Substitute into Pressure formula}\\
\\
$$p=\frac{1}{3}\rho\mathlarger{\bar{c^2}}$$
\end{document}
